A Critical Appraisal of Zero-Multiple Method in Classical Water Simulation

### 2014-10-31 writedown/zm/paper.water/main.tex
backup adding result discussion

In this work, we investigate the water system modeled by
TIP3P~\cite{jorgensen1983comparison} point-charge water model.
The size of the systems and corresponding number of molecules used for MD simulations are summarized in Tab.~\ref{tab:tmp1}.
The benchmark quantities were calculated in either  canonical (NVT) or isothermal-isobaric (NPT) ensemble.
In order to equilibriate the temperature,
the systems were coupled to either Nose-Hoover~\cite{nose1984molecular,hoover1985canonical} or Langevin thermostat (Tab.~\ref{tab:tmp1})
at 300~K.
In the NPT simulations, the systems were further coupled
to the Parrinello-Rahman barostat~\cite{parrinello1980crystal,parrinello1981polymorphic} (in Gromacs implementation)
with time-scale $\tau_P = 0.5$~ps to equilibriate the system at 1~Bar.
All systems were integrated with leap-frog scheme at the time-step of 0.001~ps.
For the ZM and SPME methods,
the neighbor lists were updated every 5 time-steps.
The ``\texttt{group}'' cut-off scheme in Gromacs was used. In order to mimic the atomistic
cut-off manner, the radius for neighbor list building was set 0.3~nm
larger than the cut-off radius (the maximum of Coulomb cut-off and the van der Waals cut-off).
To make sure the van der Waals interactions were cut-off in a smooth way,
they are modified in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs ``\texttt{shift}'' method.
The short-range part of SPME method is also smoothed in a shell of $0.05$~nm width  by the Gromacs ``\texttt{pme-switch}'' method.
The reciprocal space
grid spacing is 0.06~nm. The B-Spline interpolation order is 6. The
splitting parameter is optimized by the error estimate for the SPME method~\cite{wang2010optimizing}.
In the simulations of the RF method, the interactoins were cut-off in the group manner,
so the radius for neighbor list building is set identical to the cut-off radius.
No cut-off smoothing was applied in the cases of RF simulation.

@@

The smallest system $\systemsb$ was adopted,
because for the quantities that are computed  by estimating fluctuations (in this
work heat capacities, compressibility, thermal expansion coefficient, dielectric constant, diffusion constant and
viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}), simply increase the size of the
system does not improve the accuracy of the 
simulation~\cite{milchev1986fluctuations,ferrenberg1991statistical}.
The optimal way of measuring these properties
is to simulate with smaller systems (as far as the finite size effect is negligible) and run longer simulations for longer time-averages.
The reason of using Nose-Hoover thermostat is that
it perturbs the dynamics of the system only slightly, while the
Langevin thermostat is likely to substantially change the dynamics
when the coupling is very strong, therefore, the former was used in computing the dynamical
properties like the diffusion constant and viscosity.
The quantities that
are ensemble averages (in this work, pressure, chemical potential, radial distribution function and Kirkwood-G factor are of this type)
were computed by the largest system $\systemlb$,
in order to achieve higher parallel efficiency.
The system $\sustemmb$ is simulated to investigate the size-dependency of the
Kirkwood-G factor~\cite{vanderSpoel2006origin}.

@@

The results are plotted in Fig.~\ref{fig:tmp0}. All pressure calculations are done with system $\systemla$.
\begin{figure}
  \centering
  \includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
  \caption{The pressure convergence with respect to the cut-off radius.
    For ZM method, the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
  }
  \label{fig:tmp0}
\end{figure}

\begin{sidewaystable}
  \centering
  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$, viscosity $\eta$, constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
    thermal expansion coefficient $\alpha$
    calculated by different methods.    
    The parenthesises in the last column show the statistical uncertainty
    at the confidence level of 95~\%.
    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
  }
  \bigskip
  \centering\small\setlength\tabcolsep{2pt}
  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}cccc cccccccc}\hline\hline
    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ & $C_{p,m}$ &   $\kappa_T$  &$\alpha$ &  $\eps$ & $D$ &  $\eta$  \\
                & [nm] & & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & [J/(mol K)] & [$10^{-10}\textrm{m}^2/\textrm{N}$] &  [$10^{-3}\textrm{K}^{-1}$]&  & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$]  \\
                &    &    &    &NVT $\systemla$&NVT $\systemsb$&  NPT $\systemsb$          &  NPT $\systemsb$    &  NPT $\systemsb$    & NVT $\systemsb$& NVT $\systemsb$    & NVT $\systemsb$       \\\hline
    SPME        &1.9 & -- &2.1 & $-26.1$ (0.2) & 72.2 (1.0)  &79.2 (0.9)           & 5.94 (0.05)               &1.03 (0.02)          & 98 (3)          &         5.86  (0.07)&         0.315  (0.007)\\
    RF          &1.2 & -- &--  & $-26.0$ (0.3) & 72.3 (0.8)  &\textbf{82.3} (1.0)  & \textbf{6.51} (0.06)      &\textbf{1.15} (0.02) & \textbf{59} (1) & \textbf{6.27} (0.19)& \textbf{0.449} (0.020)\\\hline
    ZM          &1.2 & 1  &0.0 & $-26.2$ (0.3) & 71.8 (0.9)  &78.9 (1.0)           & 5.87 (0.05)               &1.01 (0.02)          & 96 (2)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)\\ 
    ZM          &1.2 & 1  &0.5 & $-26.4$ (0.3) & 72.3 (0.8)  &78.9 (0.9)           & 5.92 (0.05)               &\textbf{1.00} (0.02) & 97 (2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)\\ 
    ZM          &1.2 & 1  &1.0 & $-26.0$ (0.2) & 72.4 (0.8)  &78.4 (0.9)           & 5.95 (0.05)               &1.01 (0.02)          & 96 (2)          &        {5.78} (0.25)& \textbf{0.330} (0.011)\\ 
    ZM          &1.2 & 1  &1.5 & $-26.0$ (0.2) & 71.3 (0.8)  &80.2 (0.9)           & 5.97 (0.05)               &1.04 (0.02)          & 99 (3)          & \textbf{5.71} (0.09)&        {0.312} (0.008)\\ 
    ZM          &1.2 & 1  &2.0 & $-26.1$ (0.3) & 71.3 (0.8)  &79.4 (0.9)           & \textbf{6.05} (0.05)      &1.05 (0.02)          & 96 (3)          &        {5.90} (0.04)&        {0.307} (0.007)\\\hline
    ZM          &1.2 & 2  &0.0 & $-26.2$ (0.2) & 71.5 (0.9)  &79.7 (1.0)           & 5.95 (0.05)               &1.03 (0.02)          & 95 (3)          &         5.82  (0.27)&         0.318  (0.012)\\
    ZM          &1.2 & 3  &0.0 & $-26.2$ (0.2) & 71.6 (0.9)  &79.5 (1.0)           & 5.99 (0.05)               &1.02 (0.02)          & 96 (3)          &         5.79  (0.09)&         0.321  (0.008)\\
    ZM          &1.2 & 4  &0.0 & $-26.0$ (0.3) & 71.1 (0.8)  &79.5 (1.0)           & 5.96 (0.05)               &1.03 (0.02)          &100 (2)          &         5.89  (0.09)&         0.318  (0.013)\\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp3}
\end{sidewaystable}

% \begin{table}
%   \centering
%   \caption{The constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
%     thermal expansion coefficient $\alpha$
%     calculated by different methods.    
%     The parenthesises in the last column show the statistical uncertainty
%     at the confidence level of 95~\%.
%     The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
%   }
%   \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cccc ccc}\hline\hline
%     Method      &   $r_c$ [nm] &    $l$ & $\alpha$ [$\textrm{nm}^{-1}$]     &  $\kappa_T$ [$10^{-10}\textrm{m}^2/\textrm{N}$] & $C_{p,m}$ [J/(mol K)] & $\alpha$ [$10^{-3}\textrm{K}^{-1}$]\\\hline
%     SPME        &  1.9     &       -- &    & 5.941 (0.050)               &79.18 (0.94)           &1.026 (0.016)          \\
%     RF          &  1.2     & --       &    & \textbf{6.508} (0.058)      &\textbf{82.34} (0.95)  &\textbf{1.149} (0.018) \\\hline
%     ZM          &  1.2     &       1  & 0.0& 5.872 (0.050)               &78.91 (0.95)           &1.009 (0.018)          \\
%     ZM          &  1.2     &       1  & 0.5& 5.920 (0.050)               &78.90 (0.92)           &\textbf{1.003} (0.016) \\
%     ZM          &  1.2     &       1  & 1.0& 5.946 (0.050)               &78.37 (0.92)           &1.008 (0.016)          \\
%     ZM          &  1.2     &       1  & 1.5& 5.974 (0.050)               &80.23 (0.86)           &1.040 (0.017)          \\
%     ZM          &  1.2     &       1  & 2.0& \textbf{6.052} (0.051)      &79.41 (0.91)           &1.045 (0.016)          \\\hline
%     ZM          &  1.2     &       2  & 0.0& 5.952 (0.051)               &79.70 (0.96)           &1.033 (0.016)          \\
%     ZM          &  1.2     &       3  & 0.0& 5.991 (0.050)               &79.49 (1.01)           &1.024 (0.019)          \\
%     ZM          &  1.2     &       4  & 0.0& 5.961 (0.054)               &79.46 (0.98)           &1.034 (0.017)          \\
%     \hline\hline
%   \end{tabular*}
%   \label{tab:tmp3a}
% \end{table}

% \begin{table}
%   \centering
%   \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$ and viscosity $\eta$
%     calculated by different methods.    
%     The parenthesises in the last column show the statistical uncertainty
%     at the confidence level of 95~\%.
%     The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
%   }
%   \begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}cccc ccccc}\hline\hline
%     Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ &  $\eps$ & $D$ &  $\eta$ \\
%                 &    [nm] &        & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & (Sys.~$\systemsb$) & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
%     % Method      &   $r_c$ [nm] &    $l$      & $\mu^\exc$ [kJ/mol] &$C_{v,m}$ [J/(mol K)] & $\eps$ (Sys.~$\systemsb$) & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] &  $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
%     SPME        &1.9 & -- &    & $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
%     RF          &1.2 & -- &--  & $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\\hline
%     ZM          &1.2 & 1  &0.0 & $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
%     ZM          &1.2 & 1  &0.5 & $-26.36$ (0.30) & 72.25 (0.78)  & 97.1 (2.2)  & \textbf{5.52} (0.25)   & \textbf{0.339} (0.008)\\ 
%     ZM          &1.2 & 1  &1.0 & $-26.01$ (0.22) & 72.44 (0.84)  & 96.2 (2.3)  &        {5.78} (0.25)   & \textbf{0.330} (0.011)\\ 
%     ZM          &1.2 & 1  &1.5 & $-26.03$ (0.24) & 71.31 (0.78)  & 99.1 (2.5)  & \textbf{5.71} (0.09)   &        {0.312} (0.008)\\ 
%     ZM          &1.2 & 1  &2.0 & $-26.14$ (0.34) & 71.27 (0.78)  & 95.9 (2.5)  &        {5.90} (0.04)   &        {0.307} (0.007)\\ \hline
%     ZM          &1.2 & 2  &0.0 & $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
%     ZM          &1.2 & 3  &0.0 & $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
%     ZM          &1.2 & 4  &0.0 & $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
%     \hline\hline
%   \end{tabular*}
%   \label{tab:tmp3}
% \end{table}
    % SPME        &         1.9     &       --      & 1.67049 (0.00014)     $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
    % RF          &         1.2     & --            & 1.66733 (0.00016)      $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\
    % ZM          &         1.2     &       1       & 1.67052 (0.00022)     $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
    % ZM          &         1.2     &       2       & 1.67029 (0.00013)     $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
    % ZM          &         1.2     &       3       & 1.67024 (0.00018)     $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
    % ZM          &         1.2     &       4       & 1.67031 (0.00010)     $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
% \subsubsection{Hydrogen bonding}
% We count

\begin{table}
  \centering
  \caption{A list of the dielectric constant calculated for different systems by different methods.
    The parameters are provided. The parenthesises in the last column show the statistical uncertainty
    of the last two digits up to the confidence level of 95~\%.}
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
    System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
    $\systemmb$  &       ZM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
    $\systemmb$  &       ZM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
    $\systemmb$  &       ZM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
    $\systemmb$  &       ZM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
    $\systemmb$  &       ZM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
    $\systemmb$  &       ZM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
    $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
    $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
    $\systemlb$  &       ZM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
    $\systemlb$  &       ZM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
    $\systemlb$  &       ZM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
    $\systemlb$  &       ZM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
    $\systemlb$  &       ZM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
    $\systemlb$  &       ZM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
    $\systemlb$  &       ZM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
   $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
    $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp2}
\end{table}

\begin{figure}
  \centering
  \includegraphics[]{fig/result.nvt/fig-rdf.eps}  
  \caption{The RDF of different method. The insert is a zoom-in of range 0.9 -- 1.5~nm. In the insert, the position of the cut-off (1.2~nm) is indicated by a vertical black line.}
  \label{fig:rdf}
\end{figure}

@@

The
resulting slop is used to calculate the diffusion constant. The results are listed in Table~\ref{tab:tmp3}.
The ZM method $l\geq 2$ is consistent with the SPME
result, while the RF method is off.

@@

The dielectric constant can be estimated in a direct manner:
\begin{align}
  \eps = 1 + \frac{1}{3L^3 k_BT} ( \langle \vert \vect M\vert^2\rangle - \vert\langle \vect M\rangle\vert^2 )
\end{align}
where
\begin{align}
  \vect M = \sum_i\boldsymbol\mu_i = \sum_{\alpha\in i} q_\alpha\vect r_\alpha
\end{align}
is the total dipole moment of the system. Since it is a fluctuation, the simulated system is $\systemsb$.
% The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:tmp3}.

@@

We investigate the convergence of the integral of the auto-correlation function w.r.t.~time:
\begin{align}
  I_\eta(T) = \frac{V}{k_BT}\int_0^T\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt,
\end{align}
and plot the function $I_\eta(T) $ for all method in
Fig.~\ref{fig:conv-vis}.  It is clear the integral for the RF method
converges at 6~ps, while the ZM method converges only in 2~ps, which
is consistent with the SPME result.  The value of ZM $l=1$ method is
different from the rest ZM method an SPME result.
The values listed  in Table~\ref{tab:tmp3} are computed with $I_\eta(10\,\textrm{ps})$.
The
system for simulation is $\systemsb$.

>>>>

In this work, we investigate the water system modeled by
TIP3P~\cite{jorgensen1983comparison} point-charge water model.
All simulations were performed by Gromacs~4.6~\cite{hess2008gromacs, pronk2013gromacs} complied by GNU C compiler with single float precision.
The size of the systems and corresponding number of molecules used for MD simulations are summarized in Tab.~\ref{tab:tmp1}.
The benchmark quantities were calculated in either  canonical (NVT) or isothermal-isobaric (NPT) ensemble, with equilibrium temperature $T=300$~K.
In order to simulate at the desired temperature,
the systems $\systemsb$ and $\systemsbp$ were coupled to either Nose-Hoover~\cite{nose1984molecular,hoover1985canonical} thermostat with time-scale $\tau_T = 1.0$~ps,
while systems $\systemmb$, $\systemmbp$, $\systemla$, $\systemlb$ and $\systemlbp$ were coupled to Langevin thermostat with time-scale $\tau_T = 0.1$~ps.
In the NPT simulations, the systems were further coupled
to the Parrinello-Rahman barostat~\cite{parrinello1980crystal,parrinello1981polymorphic} (in Gromacs implementation)
with time-scale $\tau_P = 0.5$~ps to equilibriate the system at 1~Bar.
All systems were integrated with leap-frog scheme at the time-step of 0.001~ps.
For the ZM and SPME methods,
the neighbor lists were updated every 5 time-steps.
The ``\texttt{group}'' cut-off scheme in Gromacs was used. In order to mimic the atomistic
cut-off manner, the radius for neighbor list building was set 0.3~nm
larger than the cut-off radius (the maximum of Coulomb cut-off and the van der Waals cut-off).
To make sure the van der Waals interactions were cut-off in a smooth way,
they are modified in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs ``\texttt{shift}'' method.
The short-range part of SPME method is also smoothed in a shell of $0.05$~nm width  by the Gromacs ``\texttt{pme-switch}'' method.
The reciprocal space
grid spacing is 0.06~nm. The B-Spline interpolation order is 6.
These parameters are chosen to be more accurate than the Gromacs default choices (grid spacing 0.12~nm and interpolation order 4).
The splitting parameter is optimized by the error estimate for the SPME method~\cite{wang2010optimizing}.
The optimized real space and reciprocal space force computing errors are both $1.4\times10^{-4}$~kJ/(mol nm).
In the simulations of the RF method, the interactoins were cut-off in the group manner,
so the radius for neighbor list building is set identical to the cut-off radius.
No cut-off smoothing was applied in the cases of RF simulation.

@@

The smallest system $\systemsb$ was adopted,
because for the quantities that are computed  by estimating fluctuations (in this
work heat capacities, compressibility, thermal expansion coefficient, dielectric constant, diffusion constant and
viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}), simply increase the size of the
system does not improve the accuracy of the 
simulation~\cite{milchev1986fluctuations,ferrenberg1991statistical}.
The optimal way of measuring these properties
is to simulate with smaller systems (as far as the finite size effect is negligible) and run longer simulations for longer time-averages.
The reason of using Nose-Hoover thermostat is that
it perturbs the dynamics of the system only slightly, while the
Langevin thermostat is likely to substantially change the dynamics
when the coupling is very strong, therefore, the former was used in computing the dynamical
properties like the diffusion constant and viscosity.
The quantities that
are ensemble averages (in this work, pressure, chemical potential, radial distribution function and Kirkwood-G factor are of this type)
were computed by the largest system $\systemlb$,
in order to achieve higher parallel efficiency.
The system $\systemmb$ is simulated to investigate the size-dependency of the
Kirkwood-G factor~\cite{vanderSpoel2006origin}.

@@

In this section we compare the benchmark quantities of the ZM method
to the SPME method to investigate the accuracy of the former.
The comparison to the RF method will also be mentioned, to show that
the ZM is a promising replacement of the RF method.

\subsection{Thermodynamic properties}

\begin{figure}
  \centering
  \includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
  \caption{The pressure convergence with respect to the cut-off radius.
    The ZM methods with order from 1 to 4 are compared with the RF. 
    The splitting parameter of ZM method is set to be $\alpha = 0.00\,\textrm{nm}^{-1}$.
    The black solid line indicates the maganitude  of the correct pressure: 1~Bar.
    The error bars present the statistical uncertainty at 95\% confidence level.
  }
  \label{fig:pres-comp}
\end{figure}

The equilibrium density of the system was determined by an NPT SPME
simulation.  In the NVT simulation the SPME electrostatic, computed
pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of
1.0~Bar.  The accuracy of ZM method, can be investigate by checking if
the NVT pressure is consistent with the target pressure.  In
Fig.~\ref{fig:pres-comp}, the pressure calculated by ZM method of
order $l=1,2,3$ and 4 are plotted against the cut-off radius.
All the  simulations are done with system $\systemla$.
It is concluded from the Figure that all ZM methods converges to the
target pressure at large enough cut-off radius.
ZM $l=1$ converges from an under-estimate of the pressure, while ZM $l=2,3$ and 4 converges
from an over-estimate.
The higher order of ZM presents an larger error in the pressure calculation than
the lower order ZM method. The ZM method is also compared with
the RF method using the experimental dielectric constant $\varepsilon_{\textrm{rf}} = 80$, 
from which it is concluded that the accuracy of ZM in pressure calculation is much higher
than the RF method.
It should be noted that even with the largest system of 13824 water molecules,
the fluctuation (measured by standard deviation) of the pressure is roughly 100~Bar, which means that it is
very difficult achieve very accurate estimate for this quantity. In practice a pressure error of 20~Bar is
still acceptable.

\begin{sidewaystable}
  \centering
  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$, viscosity $\eta$, constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
    thermal expansion coefficient $\alpha$
    calculated by different methods.    
    The parenthesises in the last column show the statistical uncertainty
    at the confidence level of 95~\%.
    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
  }
  \bigskip
  \centering\small\setlength\tabcolsep{2pt}
  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}cccc cccccccc}\hline\hline
    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ & $C_{p,m}$ &   $\kappa_T$  &$\alpha$ &  $\eps$ & $D$ &  $\eta$  \\
                & [nm] & & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & [J/(mol K)] & [$10^{-10}\textrm{m}^2/\textrm{N}$] &  [$10^{-3}\textrm{K}^{-1}$]&  & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$]  \\
                &    &    &    &NVT $\systemla$&NVT $\systemsb$&  NPT $\systemsb$          &  NPT $\systemsb$    &  NPT $\systemsb$    & NVT $\systemsb$& NVT $\systemsb$    & NVT $\systemsb$       \\\hline
    SPME        &1.9 & -- &2.1 & $-26.1$ (0.2) & 72.2 (1.0)  &79.2 (0.9)           & 5.94 (0.05)               &1.03 (0.02)          & 98 (3)          &         5.86  (0.07)&         0.315  (0.007)\\
    RF          &1.2 & -- &--  & $-26.0$ (0.3) & 72.3 (0.8)  &\textbf{82.3} (1.0)  & \textbf{6.51} (0.06)      &\textbf{1.15} (0.02) & \textbf{59} (1) & \textbf{6.27} (0.19)& \textbf{0.449} (0.020)\\\hline
    ZM          &1.2 & 1  &0.0 & $-26.2$ (0.3) & 71.8 (0.9)  &78.9 (1.0)           & 5.87 (0.05)               &1.01 (0.02)          & 96 (2)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)\\ 
    ZM          &1.2 & 1  &0.5 & $-26.4$ (0.3) & 72.3 (0.8)  &78.9 (0.9)           & 5.92 (0.05)               &\textbf{1.00} (0.02) & 97 (2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)\\ 
    ZM          &1.2 & 1  &1.0 & $-26.0$ (0.2) & 72.4 (0.8)  &78.4 (0.9)           & 5.95 (0.05)               &1.01 (0.02)          & 96 (2)          &        {5.78} (0.25)& \textbf{0.330} (0.011)\\ 
    ZM          &1.2 & 1  &1.5 & $-26.0$ (0.2) & 71.3 (0.8)  &80.2 (0.9)           & 5.97 (0.05)               &1.04 (0.02)          & 99 (3)          & \textbf{5.71} (0.09)&        {0.312} (0.008)\\ 
    ZM          &1.2 & 1  &2.0 & $-26.1$ (0.3) & 71.3 (0.8)  &79.4 (0.9)           & \textbf{6.05} (0.05)      &1.05 (0.02)          & 96 (3)          &        {5.90} (0.04)&        {0.307} (0.007)\\\hline
    ZM          &1.2 & 2  &0.0 & $-26.2$ (0.2) & 71.5 (0.9)  &79.7 (1.0)           & 5.95 (0.05)               &1.03 (0.02)          & 95 (3)          &         5.82  (0.27)&         0.318  (0.012)\\
    ZM          &1.2 & 3  &0.0 & $-26.2$ (0.2) & 71.6 (0.9)  &79.5 (1.0)           & 5.99 (0.05)               &1.02 (0.02)          & 96 (3)          &         5.79  (0.09)&         0.321  (0.008)\\
    ZM          &1.2 & 4  &0.0 & $-26.0$ (0.3) & 71.1 (0.8)  &79.5 (1.0)           & 5.96 (0.05)               &1.03 (0.02)          &100 (2)          &         5.89  (0.09)&         0.318  (0.013)\\
    \hline\hline
  \end{tabular*}
  \label{tab:thermo}
\end{sidewaystable}

Ohter thermodynamic quantities including the chemical potential,
constant volume/pressure molar heat capacity, isothermal
compressibility and heat expansion coefficient are compared in
Tab.~\ref{tab:thermo}.
The ZM results are in good consistency with the SPME results, and out-perform
the RF method.

\recheck{Discussion of the energy correction in the chemical potential calculation. TO be added later}

% \begin{table}
%   \centering
%   \caption{A list of the dielectric constant calculated for different systems by different methods.
%     The parameters are provided. The parenthesises in the last column show the statistical uncertainty
%     of the last two digits up to the confidence level of 95~\%.}
%   \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
%     System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
%     $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
%     $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
%    $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
%     $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
%     \hline\hline
%   \end{tabular*}
%   \label{tab:tmp2}
% \end{table}

\subsection{Radial distribution function}

\begin{figure}
  \centering
  \includegraphics[]{fig/result.nvt/fig-rdf.eps}  
  \caption{The comparison of the center-of-mass radial distribution functions
    calculated by SPME, ZM and RF methods. The insert is a zoom-in of
    range 0.9 -- 1.5~nm. In the insert, the position of the cut-off
    (1.2~nm) is indicated by a vertical black line.
    For ZM method, the splitting parameter $\alpha$ was set to 0.
  }
  \label{fig:rdf}
\end{figure}

We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution functions (RDFs) of TIP3P water
calculated by the SPME, ZM ($l=1,2,3$ and 4) and RF method.  The RDFs
are computed from NVT simulations of system $\systemlb$. It is
observed from the Figure that the ZM RDFs are consistency very well
with the SPME RDF, except an artificial oscillation around the
cut-off radius. Higher orders of ZM method present lower oscillation, and when
$l\geq 3$, the oscillation is almost negligible. Therefore, for the sake
of high accuracy RDF computation, the ZM method of order at least 3 should be used.

\recheck{Shall we comment here on the fact that group cut-off produces smoother RDF?}

\subsection{Dielectric quantities}

@@

The
resulting slop is used to calculate the diffusion constant. The results are listed in Table~\ref{tab:thermo}.
The ZM method $l\geq 2$ is consistent with the SPME
result, while the RF method is off.

@@

The dielectric constant can be estimated in a direct manner:
\begin{align}
  \eps = 1 + \frac{1}{3L^3 k_BT} ( \langle \vert \vect M\vert^2\rangle - \vert\langle \vect M\rangle\vert^2 )
\end{align}
where
\begin{align}
  \vect M = \sum_i\boldsymbol\mu_i = \sum_{\alpha\in i} q_\alpha\vect r_\alpha
\end{align}
is the total dipole moment of the system. Since it is a fluctuation, the simulated system is $\systemsb$.
% The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:thermo}.

@@

We investigate the convergence of the integral of the auto-correlation function w.r.t.~time:
\begin{align}
  I_\eta(T) = \frac{V}{k_BT}\int_0^T\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt,
\end{align}
and plot the function $I_\eta(T) $ for all method in
Fig.~\ref{fig:conv-vis}.  It is clear the integral for the RF method
converges at 6~ps, while the ZM method converges only in 2~ps, which
is consistent with the SPME result.  The value of ZM $l=1$ method is
different from the rest ZM method an SPME result.
The values listed  in Table~\ref{tab:thermo} are computed with $I_\eta(10\,\textrm{ps})$.
The
system for simulation is $\systemsb$.
